Multiprocessing air palletization and tour planning for simultaneous pickup and delivery

### 2022-11-10 latex/comp_or.tex
Edges heuristic calculation changed

The selection of edges for $E^N_k$\/ uses the {\it edge attractiveness}\/ $\theta^k_{ij}$\/ \ref{eq:edge}, which can be understood as the tendency to allocate the item $t^k_j$\/ to the pallet $p_i$. It is directly proportional to the score, and inversely proportional to the volume and the torque of each item.

\begin{equation} \label{eq:edge}
	\theta^k_{ij}= \frac{t^k_j.s}{t^k_j.v}\times(1-\frac{t^k_j.w\times|p_i.d|}{\max_s\{t^k_s.w\}\times\max_q\{|p_q.d|\}});\ i \in \{1,2,\ldots,m\},\ j \in \{1,2,\ldots,n_k\}
\end{equation}

@@

Below, we present five implementations for $SolveNode$: the first using a MIP solver, and four with developed heuristics: {\it Ant Colony Optimization}\/ (ACO), {\it Multiprocessed Ant Colony Optimization}\/ (ACO-p),  and {\it Shims},  and {\it Multiprocessed Shims (Shims-p)}.

@@

In the tests performed, we used a 64-bit, 128GiB, 3.6GHz, 48-core processor, 2 threads per core, Intel(R) Xeon(R), with {\it Linux CentOS 8} as the operational system and {\it Python 3.10.4}\/ as the programming language. We also used the well-known solver {\it Gurobi}\/ (www.gurobi.com), version 9.5.2.

@@

\begin{table}[H]
	\centering
	\caption{Methods and scenarios with $volume=1.2$}  \label{tab:20}
	\footnotesize
	\begin{tabular}{l|c|cccccc|c}
		\toprule
		{$method$}                        & {\bf Results}    & {\bf 1}     &  {\bf 2}    & {\bf 3}      & {\bf 4}      & {\bf 5}      & {\bf 6}     & \specialcell{{\bf Normalized}\\{\bf Speed-up}} \\
		\toprule

		\multirow{2}{*}{\textbf{Shims}}   & $f$              & 6.24        & 4.07        &          &          &          &         &   \\ 
		                                  &{\bf run-time (s)}& <1          & 1           &             &            &            &          &   \\ %206s
		\midrule[.1pt]

		\multirow{2}{*}{\textbf{Shims-p}} & $f$              & 6.59        & 3.95        &          &          &          &         &   \\ 
		                                  &{\bf run-time (s)}& 2           & 12          &             &            &            &          &   \\ %299s
		\midrule[.1pt]

		\multirow{2}{*}{\textbf{ACO}}     & $f$              & 6.05        &         &          &        &       &      &   \\ 
                                          &{\bf run-time (s)}& 26          &          &           &        &       &      &   \\ 
        \midrule[.1pt]

        \multirow{2}{*}{\textbf{ACO-p}}   & $f$              & 5.90        &         &          &         &       &       &   \\ 
                                          &{\bf run-time (s)}& 12          &           &           &         &       &       &   \\

@@

>>>>

The selection of edges for $E^N_k$\/ uses the {\it edge attractiveness}\/ $\theta^k_{ij}$\/ \ref{eq:edge}, which can be understood as the tendency to allocate the item $t^k_j$\/ to the pallet $p_i$. It is directly proportional to the score, and inversely proportional to the volume and the torque of each item. The 3000 value was empirically set to keep the attractiveness in the range [0, 1], to be compatible with the Ant Colony Optimization pheromone range.

\begin{equation} \label{eq:edge}
	\theta^k_{ij}= \frac{t^k_j.s}{t^k_j.v \times 3000}\times(1-\frac{t^k_j.w\times|p_i.d|}{\max_s\{t^k_s.w\}\times\max_q\{|p_q.d|\}});\ i \in \{1,2,\ldots,m\},\ j \in \{1,2,\ldots,n_k\}
\end{equation}

@@

Below, we present five implementations for $SolveNode$: the first using a MIP solver, and four with developed heuristics: {\it Ant Colony Optimization}\/ (ACO), {\it Multiprocessed Ant Colony Optimization}\/ ({\it mpACO}),  and {\it Shims},  and {\it Multiprocessed Shims (mpShims)}.

It is important to say that the parallel ACO ({\it pACO}) is a different implementation where employs threads instead of processes to solve each ant solution in parallel. We chose {\it mpACO} for our approach because of the need to share the pheromone array between ants/processes and the facility to handle the possibility of race condition.

@@

All the experiments are performed on a 64-bit, 128GiB, 3.6GHz, 48-core processor, 2 threads per core, Intel Xeon, with {\it Linux CentOS 8} as the operational system and {\it Python 3.10.4}\/ as the programming language.

@@

\begin{table}[H]
	\centering
	\caption{Methods and scenarios with $volume=1.2$}  \label{tab:20}
	\footnotesize
	\begin{tabular}{l|c|cccccc|c}
		\toprule
		{$method$}                        &{\bf Results}    &{\bf 1}     &{\bf 2}    &{\bf 3}      &{\bf 4}      &{\bf 5}      &{\bf 6}     &\specialcell{{\bf Normalized}\\{\bf Speed-up}} \\
		\toprule

		\multirow{2}{*}{\textbf{Shims}}   & $f$              & 5.40        & 2.94        &          &          &          &         &   \\ 
		                                  &{\bf run-time (s)}& <1          & 1           &             &            &            &          &   \\ %206s
		\midrule[.1pt]

		\multirow{2}{*}{\textbf{Shims-p}} & $f$              & 5.72        & 3.17        &          &          &          &         &   \\ 
		                                  &{\bf run-time (s)}& 2           & 12          &             &            &            &          &   \\ %299s
		\midrule[.1pt]

		\multirow{2}{*}{\textbf{ACO}}     & $f$              & 5.64        &         &          &        &       &      &   \\ 
                                          &{\bf run-time (s)}& 23          &          &           &        &       &      &   \\ 
        \midrule[.1pt]

        \multirow{2}{*}{\textbf{ACO-p}}   & $f$              & {\bf 5.81}        &         &          &         &       &       &   \\ 
                                          &{\bf run-time (s)}& 16          &           &           &         &       &       &   \\

@@

\begin{figure}[H]
	\centering
	\includegraphics[scale=0.4]{Images/multithreads.png}
	\caption{sdf sdf sdf sdf}
	\small\textsuperscript{Source: sdfsdf}
	\label{fig:multithreads}
\end{figure}
